\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\LARGE Naufal Fikri Setiawan}\\
    naufal@naufik.net -- https://naufik.net
\end{center}


%-----------EDUCATION-----------
\vspace{-2pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {InGenious AI}{Feb 2020 -- Present}
      {Full Stack Software Engineer}{Melbourne, VIC AU}
      \resumeItemListStart
        \resumeItem{Develop and maintain features for the InGenious AI chatbot platform. Written in Javascript.}
        \resumeItem{Develop and maintain pipelines for machine learning operations. Written in Python.}
        \resumeItem{Monitor for platform faults and anomalies and respond to them by introducing appropriate patches.}
        \resumeItem{Perform maintenance of back-end services and their configurations via Amazon Web Services (Web and CLI).}
        \resumeItem{Introduced continuous development pipelines to the development workflow at InGenious AI using Bitbucket Pipelines}
        \resumeItem{Successfully added two new third party messaging integrations into the platform. Enabling InGenious AI and partnering companies to
        acquire bigger clients in terms of market share.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
    \resumeSubHeadingListStart
    \resumeSubheading
      {University of Melbourne}{Feb 2018 -- Feb 2020}
      {Tutor and Demonstrator (Casual)}{Melbourne, VIC AU}
      \resumeItemListStart
        \resumeItem{Delivered materials for many classes at various levels to students in person while also assisting beyond the classroom via an online system.}
        \resumeItem{Marked assignments objectively according to rubrics and ensuring that grades and feedback are delivered to students in a timely manner while being constructive.}
        \resumeItem{Classes delivered:
            \begin{itemize}
                \item \emph{Introduction to Programming}. Teaches basic programming at Master's Level, focused on students diverting from other disciplines to pursue a postgraduate degree in computing. Taught using Python.
                \item \emph{Media Computation}. Teaches basic programming with a focus on design and multimedia (images, websites and animations). Taught using Python.
                \item \emph{Object Oriented Software Development}. Introduces data modelling and designing abstractions for object-oriented software. Taught using Java.
                \item \emph{Models of Computation}. Penultimate subject teaching theoretical computer science concepts such as formal languages, automatons and Turing machines. Taught using Haskell.
            \end{itemize}
        }
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
    \resumeSubHeadingListStart
    \resumeSubheading
      {University of Melbourne}{Jul 2019 -- Nov 2019}
      {Research Assistant (Casual)}{Melbourne, VIC AU}
      \resumeItemListStart
        \resumeItem{Formulated a proof-of-concept for database indexing.}
        \resumeItem{Received honorable mention for "Best Student Paper Award".}
        \resumeItem{Designed and executed experiments to evaluate different approaches to model data primarily using PyTorch, Python, and Wolfram Mathematica.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
      \resumeSubHeadingListStart
    \resumeSubheading
      {Nodeflux}{Jan 2018 -- Feb 2018}
      {Software Engineer Intern (Full Time)}{Jakarta, Indonesia}
      \resumeItemListStart
        \resumeItem{Developed a ledger system for license activations that enables Nodeflux to sell their software and monitor client license activations. Written using Typescript.}
        \resumeItem{Modeled, designed and tested database schemas to log transactions using PostgreSQL.}
        \resumeItem{Implemented test-driven development using Typescript testing frameworks: Chai, Mocha, and Sinon.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
  
  \section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {University of Melbourne}{Jul 2016 - Jul 2019}
      {Bachelor of Science (Computing and Software Systems)}{Melbourne, VIC AU}
        \resumeItemListStart
        \resumeItem{Thesis Topic: "Function Interpolation for Learned Index Structures". Work on paper continued as casual research assistant.}
        \resumeItem{Weighted Average Mark: 79.18/100 (Second Class Honours)}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PUBLICATIONS-----------
\section{Publications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Function Interpolation for Learned Index Structures. Databases Theory and Applications. Australasian Database Conference 2020. p. 68-80.}{\\Setiawan, N., Rubinstein, B.I.P.,  Borovica-Gajic, R.}
}}
 \end{itemize}

%-----------CERTIFICATIONS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Proficient with} -- Javascript and Typescript (NodeJS), SQL, Python, Java, AWS (Container/VM Deployments)
    }}
    \small{\item{
     \textbf{Working knowledge of} -- Azure VMs, Terraform, AWS Security, C\# (.NET Core), React, Docker
    }}
 \end{itemize}

\end{document}
